Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-03-19 paper/abstraction/paper.tex
edits to 7

In this work, we focus on synthesizing configurations for a network that runs the Border Gateway Protocol (BGP), the standard for routing across independent organizations and inside large data centers. It scales effectively and allows operators to define flexible policies. We provide a brief background on BGP focused on aspects relevant to our work.

@@

All route announcements carry an {\em AS path}, the sequence of BGP speakers (called Autonomous Systems) that will be traversed to reach the destination.
%When BGP is used inside a data center, each router tends to be its own AS.
Optionally, they may also include one or more {\em communities}, which are arbitrary tags whose semantics are agreed upon out of band.

@@

To simplify network configuration, operators are adopting a template-based approach~\cite{hatch,thwack}. Instead of authoring a configuration per router, operators author a template per role.
%
A {\em role} is a specific function that is served by one or more routers.
%\footnote{If a role is played by devices from multiple vendors, there is one template per role-vendor combination because templates use vendor configuration languages.}
%
For example, the network in Figure~\ref{fig:example} might have five roles: spine, global aggregator, global ToR, local aggregator, and local ToR.
%
Figure~\ref{fig:templates} shows an example of what a small component of a template for the spine role in the two data centers might look like. The template has parameters for various aspects of the configuration (\EG, neighbor list, local prefixes) and is compiled to low-level device configurations by instantiating the parameters using the network topology and a database of network information.

@@

As described earlier (\S\ref{sec:introduction}), templates are hard to author and hard to validate. Worse, templates that work for one topology may not work for seemingly-inconsequential variations (which may arise after the network evolves).
Consider the network in Figure~\ref{fig:example2}, which is similar to Figure~\ref{fig:example}: it has the same five roles, connected in a similar hierarchy. One might think that the same templates (with different database entries) can be used for both cases. However, if the templates are configured to disallow ``valley" paths (per policy (5) above), they will work for Figure~\ref{fig:example} but silently violate the fault tolerance policy $(8)$ when used for Figure~\ref{fig:example2}.  Specifically, in Figure~\ref{fig:example2}, an aggregation-based black hole (\S\ref{sec:background}) will occur when the link S1--A1 fails; after this failure, S1 has no valley-free path to P[1--2] even though it will continue to get traffic for these prefixes as it announces the covering prefix PG (because it gets routes for P[3--4]). No such black hole will occur in Figure~\ref{fig:example} after a single link failure because spine routers have two links to each pod.

@@

Today, if operators discover their old templates no longer work, changing a template will
cause a change to all devices that use it---an unacceptable disruption in many cases.  When that happens, operators may abandon templates entirely and revert to hand-crafting configurations, using local patches to accommodate the change.
Such patches reintroduce the complexity and errors that templates were meant to prevent.

@@

\sysname takes as input the network's abstract topology and its policy. The policy has two components: the routing policy describes how traffic should flow, and the fault-tolerance policy describes how many simultaneous link failures the network can withstand without losing connectivity.

@@

The BGP routing protocol standard allows for the use of \emph{community tags}---32-bit integer tags that can be arbitrarily attached to, or removed from, routing advertisements. 
Community tags serve as a simple form of \emph{history}, and operators routinely use such tags to implement policy. For example, operators might tag advertisements at certain entry points and then block the export of tagged 
advertisements to prevent their network from becoming a transit point.

@@

Tagging and filtering according to the PG restricts the possible paths to those that are allowed by the policy. However, finding \emph{some} path to the destination is not enough. We must ensure that each router uses its \emph{best} available path to the destination according to the policy. Further, each router must continue to use its best available path as elements of the network fail. In the example from Figure~\ref{fig:example-compilation}, the policy was $\True ~\Path~ \CD{\Exit(N1\Prefer N2)}$, which indicates that paths through N1 should be used whenever possible, and paths through N2 should only be used as a backup. If router S1 allows advertisements from both N1 and N2, but does not prefer one advertisement over another, it might end up choosing to use a path through N2 even though a more preferred path through N1 exists and is available\footnote{Ties between equally preferred paths can be broken nondeterministically.}. On the other hand, if the S1-N1 link fails, then the best available path is through N2.

To enforce correct network-wide preferences, we use the BGP local-preference attribute, which allows routers to prefer routes from one neighbor (or with some tag) over routes learned from another neighbor. The challenge is to find a collection of device-local preferences that correctly enforce the policy's network-wide preferences in the face of any set of failures.

@@

In general, because BGP is distributed, each router does not have a view of the entire network when choosing which path to use, and finding a collection of preferences to ensure correct end-to-end behavior for all failures is a hard problem. \Propane introduced a conservative search strategy for determining route preferences that works well in practice. To make it work for abstract topologies, we modify the search based on the following observation about the PG structure:\footnote{Recall that $\Pref(m)$ is a set of priorities --- the priorities of the
automata whose final states include $m$.  
For instance, if $\Pref(m)$ is \{1,3\} then
automata 1 and automata 3 have $m$ as a final state.  Moreover, recall that
the policy expressed by automata $i$ is preferred to the policy expressed
by automata $j$ if $i < j$.}

@@

%
For example, in the inequality $(S1,0,1) \leq (S1,1,0)$ holds since nodes on the left side of the PG can always match transitions made on the right hand side with respect to the $\geq_{rank}$ relation. This relation does not hold the other way around since $(S1,0,1) \ngeq_{rank} (S1,1,0)$. Therefore, advertisements received at $S1$ with tag $(1,0)$ must be preferred to those received at $S1$ with tag $(0,1)$.
%
Notice that in the abstract PG $(S,0,1) \leq (S,1,0)$ also holds. This leads to the following observation:

>>>>

In this work, we focus on synthesizing configurations for a network that runs BGP, the standard for routing across independent organizations and inside large data centers. It scales effectively and allows operators to define flexible policies. We provide a brief background on BGP focused on aspects relevant to our work.

@@

All route announcements carry an {\em AS path}, the sequence of BGP networks, called autonomous systems (ASes), that will be traversed to reach the destination.
%When BGP is used inside a data center, each router tends to be its own AS.
Optionally, they may also include one or more {\em communities}, which are arbitrary tags whose semantics are agreed upon out of band.

@@

To simplify them, operators are adopting a template-based approach~\cite{hatch,thwack}. Instead of authoring a configuration per router, operators author a template per role.
%
A {\em role} is a specific function that is served by one or more routers.
%\footnote{If a role is played by devices from multiple vendors, there is one template per role-vendor combination because templates use vendor configuration languages.}
%
For example, the network in Figure~\ref{fig:example} might have five roles: spine, global aggregator, global ToR, local aggregator, and local ToR.
%
Figure~\ref{fig:templates} shows an example of what a small component of a template for the spine role in the two data centers might look like. The template has parameters for various aspects of the configuration (\EG, neighbor list, local prefixes) and is compiled to low-level device configurations by instantiating the parameters using the network topology and a database of network information.

@@

As described earlier (\S\ref{sec:introduction}), templates are hard to author and hard to validate. Worse, templates that work for one topology may not work for seemingly-inconsequential variations which may arise after the network evolves.
Consider the network in Figure~\ref{fig:example2}, which is similar to Figure~\ref{fig:example}; it has the same five roles, connected in a similar hierarchy. One might think that the same templates, with different database entries, can be used for both cases. However, if the templates are configured to disallow ``valley" paths (per policy (5) above), they will work for Figure~\ref{fig:example} but silently violate the fault tolerance policy $(8)$ when used for Figure~\ref{fig:example2}.  Specifically, in Figure~\ref{fig:example2}, an aggregation-based black hole (\S\ref{sec:background}) will occur when the link S1--A1 fails; after this failure, S1 has no valley-free path to P[1--2] even though it will continue to get traffic for these prefixes as it announces the covering prefix PG (because it gets routes for P[3--4]). Such a black hole will not occur in Figure~\ref{fig:example} because spine routers have two links to each pod.

@@

When operators discover that an old template no longer works, they may consider changing it, which may cause a change to all devices that use it---an unacceptable disruption in many cases.  As a result, operators may abandon the template entirely and revert to hand-crafting configuration patches to accommodate the change.
Such patches reintroduce the complexity and the risk of errors that templates were meant to prevent.

@@

\sysname takes as input the network's abstract topology and its policy. The policy consists of the routing policy that describes how traffic should flow and the fault-tolerance policy that describes how many simultaneous link failures the network should withstand without losing connectivity.

@@

The BGP routing protocol allows \emph{community tags}---32-bit integer tags that can be arbitrarily attached to, or removed from, routing advertisements. 
Community tags serve as a simple form of \emph{history}, and operators routinely use such tags to implement policy. For example, operators might tag advertisements at certain entry points and then block the export of tagged 
advertisements to prevent their network from becoming a transit point.

@@

Tagging and filtering based on the PG restricts the possible paths to those that are allowed by the policy. However, finding \emph{some} path to the destination is not enough. We must ensure that each router uses its \emph{best} available path according to the policy. Further, each router must continue to use its best available path as elements of the network fail. In the example from Figure~\ref{fig:example-compilation}, the policy was $\True ~\Path~ \CD{\Exit(N1\Prefer N2)}$, which indicates that paths through N1 should be used whenever possible, and paths through N2 should only be used as a backup. If router S1 allows advertisements from both N1 and N2, but does not prefer one advertisement over another, it might end up choosing to use a path through N2 even though a more preferred path through N1 exists and is available\footnote{Ties between equally preferred paths can be broken nondeterministically.}. On the other hand, if the S1-N1 link fails, then the best available path is through N2.

To enforce correct path preferences, we use the BGP local-preference attribute, which allows routers to prefer certain routes (e.g., those from a particular neighbor or with a tag) over other routes. The challenge is to find a collection of device-local preferences that correctly enforce the policy's network-wide preferences in the face of any set of failures.

@@

In general, because BGP is distributed, each router does not have a view of the entire network when choosing which path to use, and finding a collection of preferences to ensure correct end-to-end behavior for all failures is a hard problem. \Propane introduced a conservative search strategy for determining route preferences that works well in practice. To make it work for abstract topologies, we modify the search based on the following observation about the PG structure:\footnote{Recall that $\Pref(m)$ is a set of priorities---those of the
automata whose final states include $m$.  
For instance, if $\Pref(m)$ is \{1,3\} then
automata 1 and 3 have $m$ as a final state.  Moreover, recall that
the policy expressed by automata $i$ is preferred to the policy expressed
by automata $j$ if $i < j$.}

@@

%
For example, in Figure~\ref{fig:example-compilation} the inequality $(S1,0,1) \leq (S1,1,0)$ holds since nodes on the left side of the PG can always match transitions made on the right hand side with respect to the $\geq_{rank}$ relation. This relation does not hold the other way around since $(S1,0,1) \ngeq_{rank} (S1,1,0)$. Therefore, advertisements received at $S1$ with tag $(1,0)$ must be preferred to those received at $S1$ with tag $(0,1)$.
%
Notice that in the abstract PG $(S,0,1) \leq (S,1,0)$ also holds. This leads to the following observation:
